\documentclass[a4paper,12pt]{memoir} % Font and paper size

\input{preamble.tex} % This has all of the packages and page layout within it.

%%%%%%%	Name and Contact Information For upper left corner %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\username{Brandon S. Zerbe}
\useroccupation{Scientific Data Analyst/\\Research Software Engineer}
\userphone{1 267 515 2520}
\useremail{brandon.s.zerb@gmail.com}
\usergithub{https:/github.com/billyziege}
\userlinkedin{www.linkedin.com/in/brandon-s-zerbe}
\userscholar{https://scholar.google.com/citations?user=fh72lfAAAAAJ&hl}

%%%%%%% Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\framebreak % Move into upper left column
~
\framebreak % Move into upper left text box

\makeuserinfo

\framebreak % Move into lower left column
~
\framebreak % Move into lower left text box

\begin{itemize}[label={}, leftmargin=0pt]
  \item \large{\textbf{EDUCATION}}
    \vspace*{-0.25cm}
    \begin{itemize}[label={},leftmargin=0.5cm]
      \school{Boston University}
      \degree{PhD}
      \yearreceived{2012}
      \field{Biomedical Engineering}
      \makeeducationitem

      \school{Indiana University}
      \degree{MS}
      \yearreceived{2006}
      \field{Physics}
      \makeeducationitem

      \school{Purdue University}
      \degree{BS}
      \yearreceived{2003}
      \field{Mathematics}
      \makeeducationitem
    \end{itemize}

  \MySep

  \item \large{\textbf{SCIENCE EXPERTISE}}
    \vspace*{-0.25cm}
    \normalsize{
      \begin{itemize}[label={}, leftmargin=0.5cm]
        \item Structural Biology
        \item Biochemisty
        \item Computational Chemistry
        \item Human Population Genetics
        \item Accelerator Physics
        \item Plasma Physics
        \item Remote Sensing
      \end{itemize}
  }

  \MySep

  \item \large{\textbf{MATH/STAT}}
    \vspace*{-0.25cm}
    \normalsize{
      \begin{itemize}[label={}, leftmargin=0.5cm]
        \item Bayesian Inference
        \item Probability
        \item Stochastics
        \item Dimension Reduction
        \item Model Development
        \item Verification and Validation
      \end{itemize}
    }

  \MySep

  \item \large{\textbf{CODE EXPERIENCE}}
    \vspace*{-0.25cm}
    \normalsize{
      \begin{itemize}[label={}, leftmargin=0.5cm]
        \item Algorithm Development
        \item Code Optimization
        \item Containers
        \item Data pipelines
        \item N-Particle Simulations
        \item Grid-based Simulations
        \item Code Refactorization
      \end{itemize}
    }
\end{itemize}

\framebreak % Move into right text box
\begin{flushleft}
  \large{\textbf{CAREER OBJECTIVES}}\\
  \MySmallSep
  \normalsize{\begin{justify}
              \textit{Short-term:} Emigrate from the US with my family.\\
              \textit{Long-term:} Find a position where I am challenged by
                                  projects that require my computational, theoretical, and
                                  data analytic skills to solve real-world problems.
              \end{justify}}
                                   
                                  
  \MySep
  \MySep

  \large{\textbf{PROFESSIONAL EXPERIENCE}}

  \MySmallSep

  \prevoccupation{Scientist 3}
  \prevemployer{Los Alamos National Laboratory}
  \prevlocation{Los Alamos, NM, USA}
  \prevtime{2022 - present}
  \prevduties{
  \begin{itemize}
    \item Lead scientific efforts to validate code-base.
    \item Advised scientists on the use of algorithms for code optimization.
    \item Implemented new features in C++ code-base.
    \item Developed unit-test verification code and V\&V documentation
  \end{itemize}
  }
  \makeprevemployment

  \prevoccupation{Postdoctoral Fellow}
  \prevemployer{Michigan State University}
  \prevlocation{East Lansing, MI, USA}
  \prevtime{2018 - 2022}
  \prevduties{
  \begin{itemize}
    \item Lead research (co-PI) into experimental ultrafast electron microscopy. 
    \item Developed novel statistical analyses.
    \item Wrote Fortran simulation software and deployed it on a High-Performace Computing Cluster.
    \item Presented work at conferences, meetings, and through peer-reviewed publications.
    \item Helped mentor a student and oversaw their work toward PhD.
  \end{itemize}
  }
  \makeprevemployment

  \prevoccupation{Research Specialist}
  \prevemployer{Michigan State University}
  \prevlocation{East Lansing, MI, USA}
  \prevtime{2015 - 2018}
  \prevduties{
  \begin{itemize}
    \item Helped develop and teach a course on physics for biologists. 
    \item Conducted research into collective effects in accelerator physics.
    \item Presented work at conferences, meetings, and through peer-reviewed publications..
  \end{itemize}
  }
  \makeprevemployment

  \prevoccupation{Research Scientist}
  \prevemployer{University of California, San Francisco}
  \prevlocation{San Francisco, CA, USA}
  \prevtime{2012 - 2015}
  \prevduties{
  \begin{itemize}
    \item Project lead on the development and deployment of a Clinical Next Generation Sequencing analysis pipeline.
    \item Wrote software handling automated pipeline tasks.
    \item Worked with and secured HIPAA-protected data.
  \end{itemize}
  }
  \makeprevemployment

\end{flushleft}
\end{document}
